Nilpotent Invariants \\ for Generic Discrete Series of Real Groups

### 2025-12-22 revision_whittaker.tex
Adds missing references

\begin{exampleplain} If $G(\R)$ is the symplectic group $\mathrm{Sp}(2n, \R)$, then $Q \simeq \Z/2\Z$ and there are two distinct Whittaker data for $G(\R)$. If $\Pi$ is the $L$-packet of discrete series with the same infinitesimal character as the trivial representation, then $\Pi_{\mathrm{gen}}$ has two elements, and the correspondence $\pi \mapsto \Wh(\pi)$ in Theorem~\ref{th:main} was made explicit by Mœglin and Renard \cite[Proposition~4.1]{moeglin_renard} following work of Wallach~\cite{wallach} and Oda~\cite{oda}. As we shall see their result agrees with the description in Section~\ref{sec:alternate_WF} below. \textcolor{red}{[/NEW]}\end{exampleplain}

>>>>

\begin{exampleplain} \textcolor{red}{[NEW]} If $G(\R)$ is the symplectic group $\mathrm{Sp}(2n, \R)$, then $Q \simeq \Z/2\Z$ and there are two distinct Whittaker data for $G(\R)$. If $\Pi$ is the $L$-packet of discrete series with the same infinitesimal character as the trivial representation, then $\Pi_{\mathrm{gen}}$ has two elements, and the correspondence $\pi \mapsto \Wh(\pi)$ in Theorem~\ref{th:main} was made explicit by Mœglin and Renard \cite[Proposition~4.1]{moeglin_renard}, based on work of Wallach~\cite{wallach} and Oda~\cite{oda} for $n=1,2$. As we shall see their result agrees with the description in Section~\ref{sec:alternate_WF} below. \textcolor{red}{[/NEW]}\end{exampleplain}
